$jk$-means tests

### 2016-08-29 Rmd/bigKtest.Rmd
started 1d stuff @jovo [neurodata/weekly-experiments#196]

```{r cc-setup, eval=FALSE, include=FALSE}
require(rmarkdown)
rmarkdown::render("bigKtest.Rmd")
system('open bigKtest.html')
```

@@

# Generate Data

@@

```{r p-results}
Y <- data.frame(X0, jk=jkv, kv = kv$cluster,
                mc=mcv$classification, kvpp=kvpp$cluster)

>>>>

```{r cc-run, eval=FALSE, include=FALSE}
require(rmarkdown)
rmarkdown::render("bigKtest.Rmd")
system('open bigKtest.html')
```

@@

# Generate Data 1d

Let $X \sim \sum_i^k \pi_i \mathcal{N}_i(\mu_i, \sigma^2)$. 
With $k = 10$ and $n = 1000$, $N = nk$, $\pi_i = 1/n$.

```{r cc-1genParams}
n <- 2e3
k <- 10
N <- n*k

set.seed(53)
mux <- c(seq(1,5,by=1),8, 10,15, 20, 25)

mu0 <- mux
(sigma1 <- rep(1,10))

Here are the means
```{r p-1means}
plot(mu0, col = 1:10, pch = 19, cex = 3)
```

We now generate the data with 
```{r cc-1genXs}
X0 <- data.frame(x1 = sapply(Z, function(x) rnorm(1, mu0[x], sigma1[x])), Z = Z)

head(X0[sample(dim(X0)[1]),])
dat <- X0[, 1]
```

And here are the data colored with the truth.
```{r p-1X0s}
ggCol <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00','#cab2d6','#6a3d9a')
ggplot(data = X0, aes(x=x1, y = Z, ,color = as.factor(Z))) +
  scale_color_manual(values = ggCol) + 
  geom_point(alpha = 0.5)
```

options: 
max iteration=100
convergence error tolerance = 1E-8
```{r, eval=FALSE}
K <- k
j <- 2

set.seed(2^10)
system.time(
  jk <- jkmeans::jkmeansEM(as.matrix(dat), K, j , 100, tol = 1E-8)
)
jkv <- apply(jk$zeta, 1,  function(x) which( x == max(x) ))
```

```{r cc-1km}
system.time({
  kv <- kmeans(dat, centers = mu0)
}
)
```

```{r cc-1mclust}
system.time(
  mcv <- Mclust(dat, 
              G = K, 
              modelNames="E")
)
mcv
```
# Results

```{r p-1results}
Y <- data.frame(X0, kv = kv$cluster,
                mc=mcv$classification,
                jk=jkv)

p1d <- ggplot(data = Y, aes(x=x1, y=Z)) +
  scale_color_manual(values = ggCol) 
```

```{r p-1all, echo=FALSE, fig.height=12,fig.width=16}
layoutm <- matrix(c(NA,2,NA,3,1,4,NA,NA,NA),3,3)

grid.arrange(
 p1d + geom_point(alpha = 0.25, aes(color = as.factor(Z))) +
   ggtitle("Truth"),
 p1d + geom_point(alpha = 0.25, aes(color = as.factor(mc))) +
   ggtitle("10=k, mclust"),
 p1d + geom_point(alpha = 0.25, aes(color = as.factor(kv))) +
   ggtitle("10=k-means"),
 p1d + geom_point(alpha = 0.25, aes(color = as.factor(jk))) +
   ggtitle("(2,10)=jk-means"),
 layout_matrix = layoutm
)
```

# Generate Data 2d

@@

```{r p-results}
Y <- data.frame(X0, jk=jkv, kv = kv$cluster,
                mc=mcv$classification)
